Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-09 paper/experiments.tex
minor revision

For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
used and the GP models are fitted by maximum likelihood estimations(MLE); for
the qKG and qEI methods, the ARD Matern52 kernels are used, and the GP
hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
integration are the default strategies of the qKG and qEI implementations and
it is unclear in the documentation about how to change the GP settings.

>>>>

For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
used and the GP models are fitted by maximum likelihood estimations (MLE); for
the qKG and qEI methods, the ARD Matern52 kernels are used, and the GP
hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
integration are the default strategies of the qKG and qEI implementations and
it is unclear in the documentation about how to change the GP settings.
